%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Evelyn Barno} \\ \vspace{1pt}
    \small 908-878-1542 $|$ \href{mailto:barnoevelyn868@gmail.com}{\underline{barnoevelyn868@gmail.com}} $|$
    3 Timothy Lane, Hardwick, NJ
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {William Paterson University}{Wayne, NJ}
      {Bachelor of Arts in Psychology}{Sept. 2023 -- May 2026}
    \resumeSubheading
      {Sussex County Community College}{Newton, NJ}
      {Associate of Arts in Psychology}{Sept. 2021 -- May 2023}
      \resumeItemListStart
        \resumeItem{Member of National Society of Leadership \& Success}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Paraprofessional}{Aug. 2022 -- Present}
      {Blairstown Elementary School}{Blairstown, NJ}
      \resumeItemListStart
        \resumeItem{Provided one-on-one aide to five students with special needs, including those with verbal, developmental, physical, and behavioral disabilities.}
        \resumeItem{Experienced in providing support for individuals with a range of medically recognized disabilities, ensuring tailored care and assistance.}
        \resumeItem{Developed and implemented individualized education plans (IEPs), resulting in substantial progress in students' academic and social development.}
        \resumeItem{Documented student progress through daily assessments, leading to tailored interventions that improved engagement and learning outcomes.}
        \resumeItem{Collaborated with a multidisciplinary team of teachers, therapists, and families to create a positive and inclusive learning environment, earning recognition for fostering student independence and growth.}
      \resumeItemListEnd
    
    \resumeSubheading
      {Caregiver}{July 2018 -- Present}
      {Private Care}{Columbia, NJ}
      \resumeItemListStart
        \resumeItem{Provided one-on-one care for a patient with Parkinson's Disease, ensuring their daily needs were met.}
        \resumeItem{Offered social and physical support while managing medication schedules to maintain the client’s health.}
        \resumeItem{Served as the go-to caregiver, delivering timely and reliable assistance on-demand.}
      \resumeItemListEnd

    \resumeSubheading
      {Laborer/Poultry Breaker}{Sept. 2016 -- Present}
      {Voodoo Farm}{Hardwick, NJ}
      \resumeItemListStart
        \resumeItem{Performed poultry breaking and packing on a family farm while managing customer interactions.}
        \resumeItem{Experienced in handling blood and maintaining composure under high-stress conditions.}
        \resumeItem{Demonstrated efficiency and attention to detail in a fast-paced, physically demanding environment.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Additional Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Certifications}{: Youth Mental Health First Aide Certification (2024)} \\
     \textbf{Skills}{: Proficient in high-pressure environments, experienced in supporting the special needs community, and highly skilled in work ethic and time management.}
    }}
 \end{itemize}

%-----------REFERENCES-----------
\section{References}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Beth Answorth, LCSW}{908.362.8211 x1406}
      {North Warren Regional School District}{\href{mailto:bansworth@northwarren.org}{bansworth@northwarren.org}}
  \resumeSubHeadingListEnd

\end{document}
